Measuring Political Freedom Around the World

### 2020-11-30 slides.Rmd
final

---
title: "Measuring Political Freedom Around the World"
subtitle: "Sabrina Ball, Joe Despres, Joe Sigler, Jacob Haywood"
date: "Last compiled `r format(Sys.time(), '%H:%M')`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

>>>>

---
title: "Measuring Political Freedom Around the World"
subtitle: "Sabrina Ball, Joe Despres, Joe Sigler, Jacob Haywood"
date: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
